### 2024-04-17 analysis/supplementary-materials/universities.Rmd

```{r}
# read in packages and datasets
install.packages("usmap")
library(usmap) #import the package
library(ggplot2) #use ggplot2 to add layer for visualization
```

@@

# Carnegie classification data 
universities <- read_excel("cc.xlsx")

# create new dataframe 
univ_and_state <- select(universities, name, state)
head(univ_and_state)

@@

# remove () from jobdata
jobdata$`University Name` <-  gsub(r"{\s*\([^\)]+\)}","",as.character(jobdata$`University Name`))

>>>>

```{r}
# read in packages and datasets
# install.packages("usmap")
library(usmap) #import the package
library(ggplot2) #use ggplot2 to add layer for visualization
```

@@

# Carnegie classification data 
universities <- readxl::read_excel("cc.xlsx")

# create new dataframe 
univ_and_state <- select(universities, name, state)
# head(univ_and_state)

@@

# remove () from jobdata
jobdata$`University Name` <- 
  gsub(r"{\s*\([^\)]+\)}",
       "",
       as.character(jobdata$`University Name`))
